---
title: "ENVIRORIGHTS TT"
subtitle: "Have rights will sustain  &#x2638;"  
author: 
  - "Project implementation: CANARI "
  - "with ICT and civic reporting support by ENVIRONMENT TOBAGO"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css"]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```
```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color =  "#3e2f5b",  
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

## trois logotipos == 3 Key logos

![all logos](https://onedrive.live.com/embed?resid=4373874DC3BD5E70%21286698&authkey=%21AGCAbGPQ8j1czCw&width=1200&height=600)

.footnote[Lets get some logos for the next slide]
---
## der Überblick == Overview 

.panelset.sideways[

.panel[.panel-name[PARTNER ENTITIES] 

![](https://onedrive.live.com/embed?resid=4373874DC3BD5E70%21288205&authkey=%21APU-Y_g0jblpzl8&width=660ENTITIES)
]

.panel[.panel-name[SPONSOR]

**The EnviroRightsTT project is funded by the European Union** (*NDICI/CSO/2023-449-480*).

]

.panel[.panel-name[DURATION]

#### 30 Months ... 
<!---- place timeline imagery here  --->--

```{r echo=FALSE, message=TRUE}
message("Timeline to be inserted here")
```
]
.panel[.panel-name[Formal ID]
<center>
<img src="https://onedrive.live.com/embed?resid=4373874DC3BD5E70%21255160&authkey=%21APZpC1eIj8dmANc&width=1024">
</center>
]]

---
## particularite&acute; == Objectives

#### Empower CSOs in T&T to:

.panelset.sideways[

.panel[.panel-name[INTERVENTION LOGIC]

#### EnviroRightsTT intervention logic hinges on the belief that empowered CSOs, with improved knowledge and capacity to utilise policy and legal mechanisms for access to information, participation and justice, can foster transparency, accountability and inclusive environmental governance in T&T.
]

.panel[.panel-name[ACCESS FOIA]

#### To effectively utilise the Freedom of Information Act (1999) to access information on environmental matters, *thereby enhancing transparency and accountability*. 
     
(*IT: Outcome 1*); 
]     
.panel[.panel-name[PARTICIPATE <br> & ADVOCATE]    
 
#### Participate in policy and *advocate for inclusive environmental governance*. 
     
(*IT: Outcome 2*); 
]    

.panel[.panel-name[SEEK JUSTICE]  
     
#### Seek justice through the mechanisms of the Environmental Commission. 
     
  (*Outcome 3*);

]

.panel[.panel-name[PROMOTE]  
     
#### Promote and foster an institutional framework and partnerships *which better enable CSOs to serve both as independent actors and partners in sustainable development*. 
     
(*IT: Outcome 4*).
 ]
]


---
##  ativitet == Activities == COMPONENT A

.panelset.sideways.right-side[

.panel[.panel-name[ MOBILISING & MAPPING]

  1. **Identifying and analysing** civil society stakeholders who are environmental defenders and advocates and should be targeted under the action. 

  1. **Analysis will look specifically at: roles and responsibilities; experiences with issues related to access to information, participation for justice in environmental matters; relationships; capacities and capacity needs** (*to identify key CSOs*). 

  1. **Mapping will inform identification** of target CSOs and development of a strategy with mechanisms for communication, engagement and capacity building under the action. 
]
]

---
## COMPONENT B / Activities

.panelset.sideways.right-side[

.panel[.panel-name[AWARENESS & CAPACITY]

**Awareness & Capacity building** will focus on several key areas, including:
    
  - Access to information  
  
  - Documenting local knowledge. 
  
  - Citizen journalism and online platform   
  
  - Legal and Scientific support 
  
  - Advocacy   
  
  - Governance      
]
]

---
## COMPONENT C   /Activities

.panelset.sideways.rightside[

.panel[.panel-name[TAKING ACTION]

CANARI will 

  ... **manage a small grant programme** to support Individual or Coalitions of CSOs, to execute their pilot actions, with support of the legal and scientific team and other partners. 

<!--
CANARI’s existing small grant programme mechanism will be used, which includes procedures for application, review, award, contracting, monitoring and reporting. CSOs will be supported to apply for and use small grants to execute pilot actions. 
-->

  ... **coach CSOs** to ensure effective implementation, financial management and reporting on the small grants. 
  
  <!-- CANARI’s extensive experience with managing small and micro grants programmes for CSOs will be leveraged to ensure a supportive approach. -->
]


]

???
 Access - EquiGov will provide training on use of the Freedom of Information Act (FOIA) to access information on environmental matters.

Mapping – CANARI will provide training in the use Participatory Information and Communication Technologies (ICTs) to collect local knowledge on environmental issues. ICTs include the use mobile phones for collection of videos and photos, using online tools including Geographic Information Systems (GIS) for storytelling, and participatory drone mapping.


This mapping and the accompanying strategy will be key resources to guide implementation of activities under other components of the action to ensure that they are targeted and effective.

 
Citizen Journalism – Environment Tobago will facilitate of writeshops and workshops for CSOs to document stories and experiences on environmental governance.  These will include topic identification, research methods, story development and review of online platforms.

Legal support – ELAW will provide raining for lawyers, scientists and CSOs on environmental law approaches and facilitate virtual exchanges for knowledge sharing and learning among CSOs, lawyers and other environmental defenders from Trinidad and Tobago and other Caribbean 
countries on experiences with environmental justice.

Advocacy – CANARI will conduct advocacy training for CSOs and facilitate virtual exchanges with CSOs from T&T and other Caribbean countries on experiences with environmental justice advocacy.

Governance – PGA will provide awareness and capacity building for Parliamentarians on the Escazú Agreement and their role in application of rights to access information, participation and access to justice in environmental matters. T&T members of parliament will also be connected with Parliamentarians from around the Caribbean who are champions for the Escazú Agreement.

---
class: inverse center middle

![](https://onedrive.live.com/embed?resid=4373874DC3BD5E70%21288503&authkey=%21AD2WKYoVumpxtxI&width=660)

.footnote[Citizen Journal, Online platform etc. | *Component B > Awareness & Capacity Building*]

---
## INTRO TO 17ASAP

```{r echo=FALSE, message=TRUE}
message( "Diagram: Civic Journal Studio [RED] > Content creators [GREEN] > Engaged CSOs [GOLD]")
```
--
```{r connorg, echo=FALSE}
DiagrammeR::grViz("orgs-connected.dot")
```

```{r echo=FALSE, message=TRUE}
message("Content == blog, podcast, mini-vids") 
```
--

```{r echo =FALSE, message=TRUE}
message("ICT == 100% Open Source") 
```
--
```{r echo=FALSE, message=TRUE}
message("STUDIO == ET Studio")
```
---
## 17ASAP's Overarching Goal:

>To strengthen civil society and citizen action in T&T for an expanded civic and democratic space 

### Key Objectives 


1. Generate timely knowledge and strategic analyses on civil society actions in relation to T&T's civic and democratic space
	
1. Coordinate targeted advocacy to defend and expand civic and democratic action for environmental rights

1. Provide WRITE SUPPORT for non-political activists and organisations advocating for sustainable approaches to development 

1. ADVOCATE FOR PROTECTION in law for activists and organisations engaged in (3) above.  

1. Strengthen public discourse on the civic space and reinforce Civil Society TT narratives via 17ASAP

1. Build VOICE (for) the most affected groups and their movements, enabling them to stimulate the fledlging environmental rights narrative in T&T - by virtue of arguing their causes.


<!--
Modified from https://www.civicus.org/documents/strategic-plan/CIVICUS-strategic-plan-2022-2027_en.pdf  -->

---

```{r message=TRUE, echo=FALSE, eval=requireNamespace("cli", quietly = TRUE)}
cli::cli_alert_success("mailto:bertrand@environmenttobago.net") 
```
--
```{r echo=FALSE, message=TRUE}
message("Almost done here")
```

---
class: center, middle

# Thanks!

Slides created by ET Studio via the R packages:
<!--
[**xaringan**](https://github.com/yihui/xaringan)<br>
[gadenbuie/xaringanthemer](https://github.com/gadenbuie/xaringanthemer)  --> 

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com)

.footnote[The Dharmachakra (&#x2638; wheel of the law with eight spokes) represents the Eightfold Path (Right View, Right Resolve, Right Speech, Right Actions, Right Occupation, Right Effort, Right Mindfulness and Right Concentration). ]

